Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures

### 2025-05-18 CCGRID Presentation/main.tex
changes

 \begin{columns}
      \column{0.05\textwidth}
        \column{0.6\textwidth}
     \begin{itemize}            
               \item Traversal $1 \rightarrow 3 \rightarrow 2$ 
             \begin{itemize}
                \item Execution of 3: $\textcolor{blue}{1000} (c_{1,2})+ \textcolor{blue}{10} (m_3) = 1011$
                \item Execution of 2: $\textcolor{blue}{1000} (m_2) + \textcolor{blue}{1} (c_{1,2}) = 1001$
            \end{itemize}
            \item Traversal $1 \rightarrow 2 \rightarrow 3$ 
            \begin{itemize}
                \item Execution of 2: $\textcolor{blue}{1000} (m_2)+ \textcolor{blue}{1} (c_{1,2}) + \textcolor{blue}{1000} (c_{1,3}) = 2001$
            \end{itemize}

@@

\begin{frame}[t]
    \frametitle{Results}
    \framesubtitle{Memory-Constrained Cluster: Relative Makespans}
         \vspace{-0.8cm}
        \begin{figure}
            \centering
            \hskip -0.8cm
            \includegraphics[scale=0.48]{diagrams/images/ms_relations_by_wf_size-constrained-barplot.png}
          %  \caption{Runtimes of HetPart2 in comparison to HetPart 1. }
        \end{figure}

    \begin{tikzpicture}[remember picture, overlay]
        \node[
            fill=white,
            draw=black,
            rounded corners,
            minimum width=4cm,
            minimum height=1.5cm,
            align=center
        ] at ([xshift=-4.0cm,yshift=-5.5cm]current page.north east)
        {Most makespans invalid, \\
        even by HEFTM-BL and HEFTM-BLC; \\ HEFTM-MM makespans the only valid ones };
    \end{tikzpicture}
   \end{frame}

>>>>

 \begin{columns}
      \column{0.01\textwidth}
        \column{0.64\textwidth}
     \begin{itemize}            
               \item Traversal $1 \rightarrow 3 \rightarrow 2$ 
             \begin{itemize}
                \item Execution of 3: \\ max ($\textcolor{blue}{1000} (c_{1,2}), \textcolor{blue}{10} (m_3))  + 1 = 1001$
                \item Execution of 2: \\ max( $\textcolor{blue}{1000} (m_2) , \textcolor{blue}{1} (c_{1,2})) = 1000$
            \end{itemize}
            \item Traversal $1 \rightarrow 2 \rightarrow 3$ 
            \begin{itemize}
                \item Execution of 2: max($\textcolor{blue}{1000} (m_2), \textcolor{blue}{1} (c_{1,2})) + \textcolor{blue}{1000} (c_{1,3}) = 2000$
            \end{itemize}

@@

\begin{frame}[t]
    \frametitle{Results}
    \framesubtitle{Memory-Constrained Cluster: Relative Makespans}
         \vspace{-0.1cm}
        \begin{figure}
            \centering
            \hskip -0.8cm
            \includegraphics[scale=0.35]{diagrams/images/ms_relations_by_wf_size-constrained-barplot.png}
          %  \caption{Runtimes of HetPart2 in comparison to HetPart 1. }
        \end{figure}

    \begin{tikzpicture}[remember picture, overlay]
        \node[
            fill=white,
            draw=black,
            rounded corners,
            minimum width=4cm,
            minimum height=1.5cm,
            align=center
        ] at ([xshift=-4.0cm,yshift=-4.8cm]current page.north east)
        {Most makespans invalid, \\
        even by HEFTM-BL and HEFTM-BLC; \\ HEFTM-MM makespans the only valid ones };
    \end{tikzpicture}
   \end{frame}
